Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-01-31 manuscript/manuscript.tex
minor stuff
ms changes

Previous work in population genomics has established that negative selection
against against new deleterious variants introduced by mutation profoundly
shapes large-scale patterns of variation across the genome. However, the
mathematical models that describe this process only consider variants so
deleterious that they cannot drift up in frequency and ultimately fix. In
reality, there number of mildly deleterious mutations

@@

@@

>>>>

Previous work in population genomics has established that negative selection
against against new deleterious variants introduced by mutation profoundly
shapes large-scale patterns of variation across the genome. However, the
mathematical models that describe this process only consider variants so
deleterious that they cannot drift up in frequency and ultimately fix. In
reality, some deleterious variants can fix if the randomness of the
evolutionary process overpowers selection. There are two primary sources of
such randomness in the evolutionary process, genetic drift and genetic draft,
but both are ignored by current mutation-selection models. Here, we introduce a
new whole-genome general mutation-selection-drift model that extends and
implements previous theory by \textcite{Santiago2016-mu}. This model estimates
the strength of selection at specified sites by modeling large-scale
distortions in chromosomal patterns of genetic variability across the genome.
Unlike previous models, our models can estimate the distribution of 
fitness effects at conserved sites. Additionally, because our 
model incorporates drift and draft, our model makes explicit predictions 
about the substitution rate of weakly deleterious mutations and allows us to 
test XXX.

A full evolutionary model of deleterious mutation must not only describe the
mutation rate and distribution of fitness effects, but also the substitution
rate for mildly deleterious mutations. Our model is fit to genome wide
patterns of genetic diversity across the genome, estimating the 
mutation rate, neutral diversity level, and the distribution of fitness effects. 
Additionally, because our model allows for substitution, our model makes 
predictions about the substitution rate in conserved features.

Previous work has established that selection against strongly deleterious
mutations across the genome profoundly shapes large-scale patterns of genetic
variability in the human genome. However,

selection against new deleterious mtuationss

In reality, natural selection in some 
parts of the genome effectively speeds up evolution, which

In
reality, the number of mildly deleterious mutations

increases the pace of ev

Here extend the theory of \textcite{Santiago2016-mu} to work across 
whole-genomes. This model estimates the reduction in genetic diversity 
from mutation-selection-drift processes

@@

emphasis on whole genome models

@@

We model the diversity at punitively neutral sites. These are sites in regions
we have \emph{a prior} reason to believe have a DFE nearly entirely
concentrated in the neutral range. While this may not be the case in reality,
it is necessary given the computational demands of modeling whole-genome
selection.
